Diminishing Democratic Ethos in South Korea by Political Dissatisfaction

### 2024-04-19 paper/paper.qmd
Update paper.qmd

In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political landscape. As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges. South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges. These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations [@article]. Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.

This paper delves into the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens. To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects. Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions and political contexts. This methodological approach allows for a detailed exploration of political satisfaction influence perceptions and behaviours related to democracy in South Korea.

The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization. By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.

@@

In the @fig-gender-perceptions, we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics. The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2'). The y-axis shows the average perception score, which likely corresponds to a survey response scale. Each bar's height indicates the average score for that perception type among the respective gender group. Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.

@@

In the @fig-age-perceptions, the same three types of perceptions are displayed. This time, however, they are categorized by birth year, which are shown on the x-axis and range from 1931 to 1997. The darkness of the bars corresponds to age, with darker shades representing older age groups.The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians. The younger generations who exhibit higher levels of distrust indicates a growing skepticism about political figures among newer generations compared to their older counterparts. This shift could reflect the evolving political landscape and the impact of recent events on the trust levels of different age groups.

@@

These figures collectively aim to shed light on the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea. The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions and political performance. Next, we will explore how these factors relate to their democratic perception through linear regression model.

@@

@fig-politicians-perceptions shows a correlation between mistrust in politicians and dissatisfaction with democracy, with a gradual upward trend line signifying that as mistrust against politicians increases, so does dissatisfaction with democracy. Notably, the younger age groups (lighter colors) seem to be concentrated at higher levels of mistrust, suggesting that younger individuals may be more inclined to distrust politicians and consequently feel more dissatisfied with democracy.

@@

The study presents an examination of how socio-economic and political dissatisfaction influence the democratic sentiments of South Koreans amidst the multifaceted challenges of globalization. By utilizing linear regression models to parse out the effects of these variables on democratic contentment, it delineates a clear pattern where political dissatisfaction holds the most sway in eroding democratic satisfaction, outpacing the influence of distrust in politicians and economic dissatisfaction. These findings illuminate the critical role of political harmony and economic stability in underpinning the health of a democracy. As South Korea faces the winds of global change, such insights are vital for crafting policies that shore up democratic integrity and public trust.

However, the research is not without limitations. It operates on the assumption that the survey responses accurately reflect the intricate reality of individual perceptions, which may not encapsulate the full spectrum of socio-political nuances. The methodology, while robust, cannot account for unmeasured variables that may confound the relationships explored. Furthermore, the cross-sectional nature of the survey data limits the ability to draw causal inferences. Despite these weaknesses, the study contributes significantly to our understanding of democracy in a rapidly evolving socio-economic landscape. It beckons a call for future research to adopt longitudinal approaches and consider a broader array of variables, thereby enriching the discourse on sustaining democratic values amidst the complexities of the modern world.

>>>>

In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political factors. As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges. South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges. These changes impact more than just the economy; they deeply influence the democratic ethos, raising important questions about the sustainability of political equality amidst pervasive transformations [@article]. Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.

This paper will explore the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens. To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects. Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions and political contexts. This methodological approach allows for a detailed exploration of political satisfaction influence perceptions and behaviours related to democracy in South Korea.

The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization. By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are important for policymakers, scholars, and citizens concerned with fostering a powerful democratic society in the face of global changes.

@@

In the @fig-gender-perceptions, we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics. The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2'). The y-axis shows the average perception score, which likely corresponds to a survey response scale. Each bar's height indicates the average score for that perception type among the respective gender groups. Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.

@@

In the @fig-age-perceptions, the same three types of perceptions are displayed. This time, however, they are categorized by birth year, which is shown on the x-axis and ranges from 1931 to 1997. The darkness of the bars corresponds to age, with darker shades representing older age groups. The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians. The younger generations who exhibit higher levels of distrust indicate a growing skepticism about political figures among newer generations compared to their older counterparts. This shift could reflect the evolving political sector and the impact of recent events on the trust levels of different age groups.

@@

These figures collectively aim to find out the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea. The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions and political performance. Next, we will explore how these factors relate to their democratic perception through linear regression model.

@@

@fig-politicians-perceptions shows a correlation between mistrust in politicians and dissatisfaction with democracy, with a gradual upward trend line signifying that as mistrust against politicians increases, so does dissatisfaction with democracy. Notably, the younger age groups (lighter colours) seem to be concentrated at higher levels of mistrust, suggesting that younger individuals may be more inclined to distrust politicians and consequently feel more dissatisfied with democracy.

@@

The study presents an examination of how socio-economic and political dissatisfaction influence the democratic sentiments of South Koreans amidst the multifaceted challenges of globalization. By utilizing linear regression models to parse out the effects of these variables on democratic contentment, it delineates a clear pattern where political dissatisfaction holds the most sway in eroding democratic satisfaction, outpacing the influence of distrust in politicians and economic dissatisfaction. These findings illuminate the critical role of political harmony and economic stability in underpinning the health of a democracy. As South Korea faces the winds of global change, such insights are vital for making policies that shore up democratic integrity and public trust.

However, the research is not without limitations. It operates on the assumption that the survey responses accurately reflect the complex reality of individual perceptions, which may not encapsulate the full spectrum of socio-political nuances. The methodology, while powerful, cannot account for unmeasured variables that may confound the relationships explored. Furthermore, the cross-sectional nature of the survey data limits the ability to draw causal inferences. Despite these weaknesses, the study contributes significantly to our understanding of democracy in a rapidly evolving socio-economic sector. It beckons a call for future research to adopt longitudinal approaches and consider a broader array of variables, thereby enriching the discourse on sustaining democratic values amidst the complexities of the modern world.
